Troopers equipped with jet packs may move further than standard troopers.
Jet packs are heavy, and troopers wearing jet packs receive a -2 AP penalty to their max AP.

It costs 3 AP to activate a jet pack.
When activating a jet pack, a trooper must move 6 to 16 dots.
A jet pack cannot be used to move fewer than 6 dots, and a jet pack can only be used once in a turn.
A jet pack can only be used outdoors.
The trooper may activate a jet pack indoors if they are next to a window or door and immediately exit the building during the flight.

A trooper can go up or down in elevation 1 level for every 3 dots they travel.
For example, if a trooper activated a jet pack to move 10 dots, then they can go up or down in elevation by up to 3 levels.
A trooper on the ground could land on the roof of a two story building by moving at least 6 dots when activating their jet pack.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{8em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Condition} & \bfseries{Modifier} \\
\Hline{1pt}
Defender Flying & +2  \\
\Hline{1pt}
\end{tabular}
\caption*{Jet Pack To Hit Modifiers}
\end{table}

If a trooper flies through an enemy firing arc, the trooper may be fired upon.
Apply a +2 modifier when targeting a flying trooper.
If the trooper receives damage that reduces their AP, they immediately fall prone on the ground.

A flying trooper may drop a hand grenade while flying, if the hand grenade is their current active weapon.
The hand grenade may be dropped on any dot the trooper flies over.
Use 5 as the base target number and resolve the attack after all troopers on your side have moved.

A trooper may remove or equip a jet pack for 5 AP, and a jet pack may be exchanged between troopers for 6 AP, like with weapons or ammunition.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{12.5em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Activity} & \bfseries{AP Cost} \\
\Hline{1pt}
Activate jet pack     & 3  \\
Remove/Equip jet pack & 5  \\
Exchange jet pack     & 6  \\
\Hline{1pt}
\end{tabular}
\caption*{Jet Pack AP Costs}
\end{table}
