Advanced movement includes both additional terrain features, such as water and barbed wire, and the option to shoot while moving.

\paragraph*{Advanced Terrain}

Some maps may offer advanced terrain features that troopers can attempt to navigate.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{9em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Movement Type} & \bfseries{AP Cost} \\
\Hline{1pt}
Change Level      & 3  \\
Rough             & 3  \\
Swamp             & 4  \\
Barbed Wire       & 6  \\
Climb Wall        & 5  \\
Enter/Exit Tunnel & 2  \\
Enter/Exit Trench & 3  \\
Shallow Water     & 4  \\
Swimming          & 4  \\
\Hline{1pt}
\end{tabular}
\caption*{Movement AP Costs}
\end{table}

The map may be marked with terrain height, such as with contour lines indicating elevation.
It costs 3 AP to change elevation by crossing a contour line.

Rough terrain and swamps slow trooper movement but otherwise function the same way as standard movement.
It costs 3 AP to move into a rough dot and 4 AP to move into a swamp dot.
Also, swamp counts as an obstruction for the purposes of resolving attacks.

Barbed wire slows trooper movement and may injure or entangle the trooper.
It costs 6 AP to enter a dot with barbed wire.
When a trooper enters a dot that has barbed wire, apply 1D6 of bludgeoning damage.
Then roll 1D6; on a result of 4-6, the trooper is entangled and cannot move further this turn.
On the trooper's next turn, roll 1D6 again to apply bludgeoning damage, then roll 1D6 to determine if the trooper remains entangled.

It costs 2 AP to enter or exit a tunnel and 3 AP to enter or exit a trench.
Moving through a trench costs standard movement AP; however, a trooper in a tunnel must crawl and movement costs double the standard AP.
A trooper in a trench counts as prone when being targeted, but a trooper in a tunnel cannot be seen or targeted by units outside of the tunnel.

Wading through shallow water costs 4 AP but is otherwise like standard movement.
Troopers must swim trough deep water.
A trooper may swim across water if they are only carrying one weapon.
For example, a trooper can only attempt to swim if they are carrying a primary or secondary weapon, but not both.
Note that a grenade launcher attached to a rifle or SMG counts as part of the primary weapon and a trooper may swim with a grenade launcher attached to a rifle or SMG.

Swimming troopers may not fire weapons or use explosives.
It costs 4 AP to move into a water dot.
Explosives do an extra 2 standard damage at each range to targets in water.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{11em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Condition} & \bfseries{Modifier} \\
\Hline{1pt}
Attacker Entangled & +1  \\
Tunnel Combat      & +2  \\
Defender Swimming  & +1  \\
\Hline{1pt}
\end{tabular}
\caption*{To Hit Modifiers}
\end{table}

\paragraph*{Movement Fire}

Troopers may use their current weapon or explosive while moving.
Movement fire attacks are resolved after any incoming fire as the trooper moves through firing arcs.
Add 2 to the target number when using movement fire.
After the attack, the trooper may continue expending AP to continue moving.

It costs 2 AP to fire a weapon using movement fire rules.
Single fire weapons can only fire once during movement fire and the trooper cannot establish a firing arc if they used movement fire with a single fire weapon.
Burst fire weapons can be fired multiple times during movement fire and the trooper may still establish a firing arc after their movement.

Troopers may use explosives with movement fire.
The trooper pays the standard AP cost for using the explosive, and the attack is still resolved at the end of the attacking side's turn.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{11em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Condition} & \bfseries{Modifier} \\
\Hline{1pt}
Movement Fire & +2  \\
\Hline{1pt}
\end{tabular}
\caption*{To Hit Modifiers}
\end{table}
