Troopers may move and take special actions prior to taking any combat actions.

\paragraph*{Basic Movement}

Troopers can use a maximum of 8 AP for movement.
Troopers move between adjacent dots on the map so long as the the new location is on valid terrain and the path between the dots does not pass though an impassible obstacle, such as a solid high wall or the truck of a tree.

Movement between adjacent dots with no obstructions between them costs 1 AP.
Movement between adjacent dots with an obstruction between costs 2 AP.
Obstructions include objects that are shorter than a person, such as furniture, light vegetation, and low walls.

Troopers may only enter and exit buildings through doorways and windows.
Movement between adjacent dots that passes through a doorway costs 2 AP.
Movement between adjacent dots that passes through a window costs 4 AP; however troopers cannot voluntarily fall out of an upper story window or off of a building.

Troopers may use stairs and ladders to change levels in or on a building.
Movement between levels costs 3 AP.
The trooper stays on the same dot when changing levels.
The current level of the trooper should be tracked on the unit card or next to the miniature.

Troopers may hide behind solid obstructions, such as furniture and low walls.
It costs 1 AP to go prone.
It costs 2 AP to stand from a prone position.
Movement while prone costs double the standard AP.

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{9em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Movement Type} & \bfseries{AP Cost} \\
\Hline{1pt}
Standard         & 1   \\
Obstructed       & 2   \\
Through door     & 2   \\
Through window   & 4   \\
Change level     & 3   \\
Go prone         & 1   \\
Stand from prone & 2   \\
Move while prone & 2x  \\
\Hline{1pt}
\end{tabular}
\caption*{Movement AP Costs}
\end{table}

\paragraph*{Special Actions}

A trooper may take the following special actions during their movement:

\begin{table}[H]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{11em} !{\Vline{1pt}} R{4.5em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Action} & \bfseries{AP Cost} \\
\Hline{1pt}
Change Weapon      & 3  \\
Exchange Equipment & 6  \\
\Hline{1pt}
\end{tabular}
\caption*{Special Action AP Costs}
\end{table}

A trooper can only have one weapon active at a time.
It costs 3 AP to change active weapons, including to change to an explosive.
A trooper automatically switches back to their primary or secondary weapon after using a grenade or satchel charge, for 0 AP.

Troopers may exchange weapons or equipment.
It costs 6 AP to take a weapon or equipment from another trooper, including a dead or unconscious trooper.
A trooper cannot exceed the basic carrying capabilities given on their unit card.
A trooper may drop weapons or equipment for 0 AP; however, any trooper, friendly or enemy, may pick up the dropped weapon or equipment.
